Monte Carlo and bootstrap for all parameters

### 2024-08-02 Draft/Draft.Rmd
Clean MC_all for CI

>>>>

## Non-optimal version of coverage rates in MC_all.Rmd ----------

```{r}
## We want all the CI based on Normal distribution obtained for each parameter of interest, 
# to find the coverage rate
CI_nb <- data.frame(useless = c(0,0))
CI_vol <- data.frame(useless = c(0,0))
CI_ratio <- data.frame(useless = c(0,0))
for (elt in res2$`Confidence Intervals`) {
  CI_nb <- cbind(CI_nb, elt$Normal$lim_nb)
  CI_vol <- cbind(CI_vol, elt$Normal$lim_vol)
  CI_ratio <- cbind(CI_ratio, elt$Normal$lim_ratio)
}
CI_nb$useless <- NULL
CI_vol$useless <- NULL
CI_ratio$useless <- NULL

CI_nb <- as.data.frame(t(CI_nb))
rownames(CI_nb) <- 1:(nrow(CI_nb))
colnames(CI_nb) <- c("x", "y")

CI_vol <- as.data.frame(t(CI_vol))
rownames(CI_vol) <- 1:(nrow(CI_vol))
colnames(CI_vol) <- c("x", "y")

CI_ratio <- as.data.frame(t(CI_ratio))
rownames(CI_ratio) <- 1:(nrow(CI_ratio))
colnames(CI_ratio) <- c("x", "y")
```

```{r}
# Check the coverage rate
TC_nb <- (1/nrow(CI_nb))*sum( mapply(function(a,b){as.numeric((29272 > a) & (29272 < b))}, CI_nb$x, CI_nb$y) )
TC_vol <- (1/nrow(CI_vol))*sum( mapply(function(a,b){as.numeric((5412.722 > a) & (5412.722 < b))}, CI_vol$x, CI_vol$y) )
TC_ratio <- (1/nrow(CI_ratio))*sum( mapply(function(a,b){as.numeric((0.1849112 > a) & (0.1849112 < b))}, CI_ratio$x, CI_ratio$y) )
cat("Concerning the normal approach, the coverage rate are the following: \n - for the number of trees: ", TC_nb, "\n - for the volume of trees: ", TC_vol, "\n - for the ratio volume / number of trees: ", TC_ratio)
```

```{r}
## We want all the Percentile CI obtained for each parameter of interest, 
# to find the coverage rate
CI_perc_nb <- data.frame(useless = c(0,0))
CI_perc_vol <- data.frame(useless = c(0,0))
CI_perc_ratio <- data.frame(useless = c(0,0))
for (elt in res2$`Confidence Intervals`) {
  CI_perc_nb <- cbind(CI_perc_nb, elt$Percentile$lim_nb)
  CI_perc_vol <- cbind(CI_perc_vol, elt$Percentile$lim_vol)
  CI_perc_ratio <- cbind(CI_perc_ratio, elt$Percentile$lim_ratio)
}
CI_perc_nb$useless <- NULL
CI_perc_vol$useless <- NULL
CI_perc_ratio$useless <- NULL

CI_perc_nb <- as.data.frame(t(CI_perc_nb))
rownames(CI_perc_nb) <- 1:(nrow(CI_perc_nb))
colnames(CI_perc_nb) <- c("x", "y")

CI_perc_vol <- as.data.frame(t(CI_perc_vol))
rownames(CI_perc_vol) <- 1:(nrow(CI_perc_vol))
colnames(CI_perc_vol) <- c("x", "y")

CI_perc_ratio <- as.data.frame(t(CI_perc_ratio))
rownames(CI_perc_ratio) <- 1:(nrow(CI_perc_ratio))
colnames(CI_perc_ratio) <- c("x", "y")
```

```{r}
# Check the coverage rate
TC_nb <- (1/nrow(CI_perc_nb))*sum( mapply(function(a,b){as.numeric((29272 > a) & (29272 < b))}, CI_perc_nb$x, CI_perc_nb$y) )
TC_vol <- (1/nrow(CI_perc_vol))*sum( mapply(function(a,b){as.numeric((5412.722 > a) & (5412.722 < b))}, CI_perc_vol$x, CI_perc_vol$y) )
TC_ratio <- (1/nrow(CI_perc_ratio))*sum( mapply(function(a,b){as.numeric((0.1849112 > a) & (0.1849112 < b))}, CI_perc_ratio$x, CI_perc_ratio$y) )
cat("Concerning the percentile approach, the coverage rate are the following: \n - for the number of trees: ", TC_nb, "\n - for the volume of trees: ", TC_vol, "\n - for the ratio volume / number of trees: ", TC_ratio)
```

```{r}
## We want all the Reverse Percentile CI obtained for each parameter of interest, 
# to find the coverage rate
CI_nb <- data.frame(useless = c(0,0))
CI_vol <- data.frame(useless = c(0,0))
CI_ratio <- data.frame(useless = c(0,0))
for (elt in res2$`Confidence Intervals`) {
  CI_nb <- cbind(CI_nb, elt$`Reverse percentile`$lim_nb)
  CI_vol <- cbind(CI_vol, elt$`Reverse percentile`$lim_vol)
  CI_ratio <- cbind(CI_ratio, elt$`Reverse percentile`$lim_ratio)
}
CI_nb$useless <- NULL
CI_vol$useless <- NULL
CI_ratio$useless <- NULL

CI_nb <- as.data.frame(t(CI_nb))
rownames(CI_nb) <- 1:(nrow(CI_nb))
colnames(CI_nb) <- c("x", "y")

CI_vol <- as.data.frame(t(CI_vol))
rownames(CI_vol) <- 1:(nrow(CI_vol))
colnames(CI_vol) <- c("x", "y")

CI_ratio <- as.data.frame(t(CI_ratio))
rownames(CI_ratio) <- 1:(nrow(CI_ratio))
colnames(CI_ratio) <- c("x", "y")
```

```{r}
# Check the coverage rate
TC_nb <- (1/nrow(CI_nb))*sum( mapply(function(a,b){as.numeric((29272 > a) & (29272 < b))}, CI_nb$x, CI_nb$y) )
TC_vol <- (1/nrow(CI_vol))*sum( mapply(function(a,b){as.numeric((5412.722 > a) & (5412.722 < b))}, CI_vol$x, CI_vol$y) )
TC_ratio <- (1/nrow(CI_ratio))*sum( mapply(function(a,b){as.numeric((0.1849112 > a) & (0.1849112 < b))}, CI_ratio$x, CI_ratio$y) )
cat("Concerning the reverse percentile approach, the coverage rate are the following: \n - for the number of trees: ", TC_nb, "\n - for the volume of trees: ", TC_vol, "\n - for the ratio volume / number of trees: ", TC_ratio)
```

### 2024-08-02 MC_all.Rmd
Clean MC_all for CI

---
title: "Monte Carlo and bootstrap for all parameters"
output: pdf_document
date: "2024-07-26"
---

@@

```{r}
coverage_rate <- function(nb){
  CI_nb <- data.frame(useless = c(0,0))
  CI_vol <- data.frame(useless = c(0,0))
  CI_ratio <- data.frame(useless = c(0,0))
  for (elt in res2$`Confidence Intervals`) {
    CI_nb <- cbind(CI_nb, c(unlist(res2$`Confidence Intervals`$CI1[1])[1], unlist(res2$`Confidence Intervals`$CI1[1])[2]))
    CI_vol <- cbind(CI_nb, c(unlist(res2$`Confidence Intervals`$CI1[1])[3], unlist(res2$`Confidence Intervals`$CI1[1])[4]))
    CI_ratio <- cbind(CI_nb, c(unlist(res2$`Confidence Intervals`$CI1[1])[5], unlist(res2$`Confidence Intervals`$CI1[1])[6]))
  }
  CI_nb$useless <- NULL
  rownames(CI_nb) <- 1:(nrow(CI_nb))
  colnames(CI_nb) <- c("x", "y")
  CI_vol$useless <- NULL
  CI_ratio$useless <- NULL

@@

```{r}
TC_normal <- coverage_rate(1)
cat("Concerning the normal approach, the coverage rates are the following: \n - for the number of trees: ", 
    TC_normal[1,1], "\n - for the volume of trees: ", TC_normal[2,1], "\n - for the ratio volume / number of trees: ", TC_normal[3,1],
    " \n \nThe parts of the estimators under the lower limit of the coverage rate are the following: \n - for the number of trees: ",
    TC_normal[1,2], "\n - for the volume of trees: ", TC_normal[2,2], "\n - for the ratio volume / number of trees: ", TC_normal[3,2],
    " \n \nThe parts of the estimators over the upper limit of the coverage rate are the following: \n - for the number of trees: ",
    TC_normal[1,3], "\n - for the volume of trees: ", TC_normal[2,3], "\n - for the ratio volume / number of trees: ", TC_normal[3,3],
    " \n \nThe mean length of coverage rates are the following: \n - for the number of trees: ",
    TC_normal[1,4], "\n - for the volume of trees: ", TC_normal[2,4], "\n - for the ratio volume / number of trees: ", TC_normal[3,4])
```

```{r}
## We want all the CI based on Normal distribution obtained for each parameter of interest, 
# to find the coverage rate
CI_nb <- data.frame(useless = c(0,0))
CI_vol <- data.frame(useless = c(0,0))
CI_ratio <- data.frame(useless = c(0,0))
for (elt in res2$`Confidence Intervals`) {
  CI_nb <- cbind(CI_nb, elt$Normal$lim_nb)
  CI_vol <- cbind(CI_vol, elt$Normal$lim_vol)
  CI_ratio <- cbind(CI_ratio, elt$Normal$lim_ratio)
}
CI_nb$useless <- NULL
CI_vol$useless <- NULL
CI_ratio$useless <- NULL

CI_nb <- as.data.frame(t(CI_nb))
rownames(CI_nb) <- 1:(nrow(CI_nb))
colnames(CI_nb) <- c("x", "y")

CI_vol <- as.data.frame(t(CI_vol))
rownames(CI_vol) <- 1:(nrow(CI_vol))
colnames(CI_vol) <- c("x", "y")

CI_ratio <- as.data.frame(t(CI_ratio))
rownames(CI_ratio) <- 1:(nrow(CI_ratio))
colnames(CI_ratio) <- c("x", "y")
```

```{r}
# Check the coverage rate
TC_nb <- (1/nrow(CI_nb))*sum( mapply(function(a,b){as.numeric((29272 > a) & (29272 < b))}, CI_nb$x, CI_nb$y) )
TC_vol <- (1/nrow(CI_vol))*sum( mapply(function(a,b){as.numeric((5412.722 > a) & (5412.722 < b))}, CI_vol$x, CI_vol$y) )
TC_ratio <- (1/nrow(CI_ratio))*sum( mapply(function(a,b){as.numeric((0.1849112 > a) & (0.1849112 < b))}, CI_ratio$x, CI_ratio$y) )
cat("Concerning the normal approach, the coverage rate are the following: \n - for the number of trees: ", TC_nb, "\n - for the volume of trees: ", TC_vol, "\n - for the ratio volume / number of trees: ", TC_ratio)
```

```{r}
## We want all the Percentile CI obtained for each parameter of interest, 
# to find the coverage rate
CI_perc_nb <- data.frame(useless = c(0,0))
CI_perc_vol <- data.frame(useless = c(0,0))
CI_perc_ratio <- data.frame(useless = c(0,0))
for (elt in res2$`Confidence Intervals`) {
  CI_perc_nb <- cbind(CI_perc_nb, elt$Percentile$lim_nb)
  CI_perc_vol <- cbind(CI_perc_vol, elt$Percentile$lim_vol)
  CI_perc_ratio <- cbind(CI_perc_ratio, elt$Percentile$lim_ratio)
}
CI_perc_nb$useless <- NULL
CI_perc_vol$useless <- NULL
CI_perc_ratio$useless <- NULL

CI_perc_nb <- as.data.frame(t(CI_perc_nb))
rownames(CI_perc_nb) <- 1:(nrow(CI_perc_nb))
colnames(CI_perc_nb) <- c("x", "y")

CI_perc_vol <- as.data.frame(t(CI_perc_vol))
rownames(CI_perc_vol) <- 1:(nrow(CI_perc_vol))
colnames(CI_perc_vol) <- c("x", "y")

CI_perc_ratio <- as.data.frame(t(CI_perc_ratio))
rownames(CI_perc_ratio) <- 1:(nrow(CI_perc_ratio))
colnames(CI_perc_ratio) <- c("x", "y")
```

```{r}
# Check the coverage rate
TC_nb <- (1/nrow(CI_perc_nb))*sum( mapply(function(a,b){as.numeric((29272 > a) & (29272 < b))}, CI_perc_nb$x, CI_perc_nb$y) )
TC_vol <- (1/nrow(CI_perc_vol))*sum( mapply(function(a,b){as.numeric((5412.722 > a) & (5412.722 < b))}, CI_perc_vol$x, CI_perc_vol$y) )
TC_ratio <- (1/nrow(CI_perc_ratio))*sum( mapply(function(a,b){as.numeric((0.1849112 > a) & (0.1849112 < b))}, CI_perc_ratio$x, CI_perc_ratio$y) )
cat("Concerning the percentile approach, the coverage rate are the following: \n - for the number of trees: ", TC_nb, "\n - for the volume of trees: ", TC_vol, "\n - for the ratio volume / number of trees: ", TC_ratio)
```

```{r}
## We want all the Reverse Percentile CI obtained for each parameter of interest, 
# to find the coverage rate
CI_nb <- data.frame(useless = c(0,0))
CI_vol <- data.frame(useless = c(0,0))
CI_ratio <- data.frame(useless = c(0,0))
for (elt in res2$`Confidence Intervals`) {
  CI_nb <- cbind(CI_nb, elt$`Reverse percentile`$lim_nb)
  CI_vol <- cbind(CI_vol, elt$`Reverse percentile`$lim_vol)
  CI_ratio <- cbind(CI_ratio, elt$`Reverse percentile`$lim_ratio)
}
CI_nb$useless <- NULL
CI_vol$useless <- NULL
CI_ratio$useless <- NULL

CI_nb <- as.data.frame(t(CI_nb))
rownames(CI_nb) <- 1:(nrow(CI_nb))
colnames(CI_nb) <- c("x", "y")

CI_vol <- as.data.frame(t(CI_vol))
rownames(CI_vol) <- 1:(nrow(CI_vol))
colnames(CI_vol) <- c("x", "y")

CI_ratio <- as.data.frame(t(CI_ratio))
rownames(CI_ratio) <- 1:(nrow(CI_ratio))
colnames(CI_ratio) <- c("x", "y")
```

```{r}
# Check the coverage rate
TC_nb <- (1/nrow(CI_nb))*sum( mapply(function(a,b){as.numeric((29272 > a) & (29272 < b))}, CI_nb$x, CI_nb$y) )
TC_vol <- (1/nrow(CI_vol))*sum( mapply(function(a,b){as.numeric((5412.722 > a) & (5412.722 < b))}, CI_vol$x, CI_vol$y) )
TC_ratio <- (1/nrow(CI_ratio))*sum( mapply(function(a,b){as.numeric((0.1849112 > a) & (0.1849112 < b))}, CI_ratio$x, CI_ratio$y) )
cat("Concerning the reverse percentile approach, the coverage rate are the following: \n - for the number of trees: ", TC_nb, "\n - for the volume of trees: ", TC_vol, "\n - for the ratio volume / number of trees: ", TC_ratio)
```

>>>>

---
title: "Monte Carlo and bootstrap for all parameters"
output: pdf_document
date: "2024-08-02"
---

@@

```{r}
coverage_rate <- function(k){
  CI_nb <- data.frame(useless = c(0,0))
  CI_vol <- data.frame(useless = c(0,0))
  CI_ratio <- data.frame(useless = c(0,0))
  for (elt in res2$`Confidence Intervals`) {
    CI_nb <- cbind(CI_nb, c(unlist(elt[k])[1], unlist(elt[k])[2]))
    CI_vol <- cbind(CI_vol, c(unlist(elt[k])[3], unlist(elt[k])[4]))
    CI_ratio <- cbind(CI_ratio, c(unlist(elt[k])[5], unlist(elt[k])[6]))
  }
  CI_nb$useless <- NULL
  # rownames(CI_nb) <- 1:(nrow(CI_nb))
  # colnames(CI_nb) <- c("x", "y")
  CI_vol$useless <- NULL
  CI_ratio$useless <- NULL

@@

```{r}
TC_normal <- coverage_rate(1)
cat("Concerning the normal approach, the coverage rates are the following: \n - for the number of trees: ", 
    TC_normal[1,1], "\n - for the volume of trees: ", TC_normal[2,1], "\n - for the ratio volume / number of trees: ", TC_normal[3,1],
    " \n\nThe parts of the estimators under the lower limit of the coverage rate are the following: \n - for the number of trees: ",
    TC_normal[1,2], "\n - for the volume of trees: ", TC_normal[2,2], "\n - for the ratio volume / number of trees: ", TC_normal[3,2],
    " \n\nThe parts of the estimators over the upper limit of the coverage rate are the following: \n - for the number of trees: ",
    TC_normal[1,3], "\n - for the volume of trees: ", TC_normal[2,3], "\n - for the ratio volume / number of trees: ", TC_normal[3,3],
    " \n\nThe mean lengths of coverage rates are the following: \n - for the number of trees: ",
    TC_normal[1,4], "\n - for the volume of trees: ", TC_normal[2,4], "\n - for the ratio volume / number of trees: ", TC_normal[3,4])
```

```{r}
TC_perc <- coverage_rate(2)
cat("Concerning the percentile approach, the coverage rates are the following: \n - for the number of trees: ", 
    TC_perc[1,1], "\n - for the volume of trees: ", TC_perc[2,1], "\n - for the ratio volume / number of trees: ", TC_perc[3,1],
    " \n\nThe parts of the estimators under the lower limit of the coverage rate are the following: \n - for the number of trees: ",
    TC_perc[1,2], "\n - for the volume of trees: ", TC_perc[2,2], "\n - for the ratio volume / number of trees: ", TC_perc[3,2],
    " \n\nThe parts of the estimators over the upper limit of the coverage rate are the following: \n - for the number of trees: ",
    TC_perc[1,3], "\n - for the volume of trees: ", TC_perc[2,3], "\n - for the ratio volume / number of trees: ", TC_perc[3,3],
    " \n\nThe mean lengths of coverage rates are the following: \n - for the number of trees: ",
    TC_perc[1,4], "\n - for the volume of trees: ", TC_perc[2,4], "\n - for the ratio volume / number of trees: ", TC_perc[3,4])
```

```{r}
TC_rev_perc <- coverage_rate(3)
cat("Concerning the percentile approach, the coverage rates are the following: \n - for the number of trees: ", 
    TC_rev_perc[1,1], "\n - for the volume of trees: ", TC_rev_perc[2,1], "\n - for the ratio volume / number of trees: ", TC_rev_perc[3,1],
    " \n\nThe parts of the estimators under the lower limit of the coverage rate are the following: \n - for the number of trees: ",
    TC_rev_perc[1,2], "\n - for the volume of trees: ", TC_rev_perc[2,2], "\n - for the ratio volume / number of trees: ", TC_rev_perc[3,2],
    " \n\nThe parts of the estimators over the upper limit of the coverage rate are the following: \n - for the number of trees: ",
    TC_rev_perc[1,3], "\n - for the volume of trees: ", TC_rev_perc[2,3], "\n - for the ratio volume / number of trees: ", TC_rev_perc[3,3],
    " \n\nThe mean lengths of coverage rates are the following: \n - for the number of trees: ",
    TC_rev_perc[1,4], "\n - for the volume of trees: ", TC_rev_perc[2,4], "\n - for the ratio volume / number of trees: ", TC_rev_perc[3,4])
```
